---
title: "Culminating Activity"
author: "Tristan, Kiarra, Joshua, Joselito, Rick"
date: ""
output: pdf_document
---

```{r, echo=FALSE, include=FALSE}
"
Ebao, Miguel Tristan Sebastian Y.
Estrada, Kiarra Ezrha P.
Juinio, Joshua Jacques Anthony L.
Yap, Joselito Jr. L.
Yuliongsiu, Rick Bryson N.
"
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Library
library(RKaggle)
library(dplyr)
library(ggplot2)
library(car)
library(lmtest)
library(olsrr)
```
# Abstract
Provide a concise summary of the study including purpose, methods, results, and conclusions (150–250 words).

# Chapter 1: Introduction

## Background of the Study
Insert text...

## Statement of the Problem
Clearly state the research questions.

1. What is the...?

## Objectives of the Study
### General Objective
- To investigate...?

### Specific Objectives
- To determine...?
- To analyze...?


## Hypotheses (if applicable)
- **H0**: There is no significant relationship between...
- **H1**: There is a significant relationship between...

## Significance of the Study
Explain who benefits and how.

## Scope and Limitations
Define the boundaries of the study.


# Chapter 2: Review of Related Literature

## Related Studies
Summarize previous research.

## Related Literature
Discuss theories and concepts.

## Conceptual Framework
(Insert diagram if needed)

```{r conceptual-framework, echo=FALSE}
# Example placeholder
# plot(1:10, 1:10, main="Conceptual Framework (Replace)")
```

# Chapter 3: Methodology

## Research Design

Describe the design (e.g., descriptive, experimental).

## Data Collection

The dataset utilized in this study was collected from Kaggle, https://www.kaggle.com/code/yonatanrabinovich/video-games-sales-regression-techniques/input.

```{r}
# Load dataset
data <- read.csv("./Video_Games_Sales_as_at_22_Dec_2016.csv",sep=",",na.strings=c(""," ","NA","N/A"))
head(data)
```

## Variables Description

Explain dependent and independent variables.

## Data Analysis Techniques

- Descriptive Statistics
- Inferential Statistics
- Machine Learning Models (if applicable)

# Chapter 4: Results and Discussion

## Descriptive Statistics

```{r, echo=FALSE}
#summary(data)
```

## Visualization
```{r}
library(ggplot2)
#ggplot(data, aes(x=Variable1, y=Variable2)) +
#  geom_point() +
#  theme_minimal()
```

## Model
```{r}
#model <- lm(total_sales~., numeric_data)
#summary(model)
```

## Interpretation

Discuss findings in paragraph form.

# Chapter 5: Conclusion and Recommendations

## Conclusion

Summarize key findings.

## **Recommendations**

Provide practical suggestions

# References

Rabinovich, Y. (2021). *Video games sales regression techniques.* Kaggle. https://www.kaggle.com/code/yonatanrabinovich/video-games-sales-regression-techniques/notebook

The Investopedia Team. (2025). *Predictive Modeling: Techniques, Uses, and Key Takeaways.* https://www.investopedia.com/terms/p/predictive-modeling.asp

# Appendices
## Appendix A: Code
