---
title: "Testing"
author: "Group 2"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(RKaggle)
library(dplyr)
library(ggplot2)
library(car)
library(lmtest)
library(olsrr)
library(DT)
library(glmnet)
library(tibble)
library(forcats)
library(purrr)
library(readr)
library(stringr)
library(corrplot)
library(mice)
library(tidyr)
library(caret)
```

## **DATA COLLECTION**

```{r, warning=FALSE}
set.seed(12)

data <- read.csv("../Video_Games_Sales_as_at_22_Dec_2016.csv",sep=",",na.strings=c(""," ","NA","N/A"))

data_row_count <- nrow(data)
```

#### Number of rows = **`r data_row_count`**

```{r, warning=FALSE}
# Show data
#head(data)
datatable(data[1:6,], 
          options = list(scrollX = TRUE, pageLength = 6),
          rownames = FALSE)


# Data cleaning
data <- na.omit(data)

na_row_count = data_row_count - nrow(data)
```

#### Number of rows with missing values = **`r na_row_count`**
#### New number of rows = **`r nrow(data)`**

```{r, warning=FALSE}
# Show data after dropping all NA values
#head(data)
datatable(data[1:6,], 
          options = list(scrollX = TRUE, pageLength = 6),
          rownames = FALSE)

str(data)

# Drop all sales except global
data_df <- cbind(data[,-c(6:10)],data$Global_Sales)
data_df$Year_of_Release <- 2016 - data_df$Year_of_Release
names(data_df)[3] <- "Game_Age"
names(data_df)[12] <- "Global_Sales"

#name column is an id column we can remove for good (only used for games Top ten sales)
data_df <- data_df[,-1]

str(data_df)

summary(data_df)
```

## **REGRESSION MODEL**

```{r, warning=FALSE}
reg_model <- data_df
str(reg_model)

# 70 : 30 RATIO
train.size <- floor(0.7*nrow(reg_model))
train.index <- sample(1:nrow(reg_model),train.size, replace = F)
train.set <- reg_model[train.index,]
test.set <- reg_model[-train.index,]
```

Train Size: **`r nrow(train.set)`**

Test Size: **`r nrow(test.set)`**

Total Size: **`r nrow(data)`**

```{r, warning=FALSE}
model <- lm(formula = Global_Sales ~ Platform + Game_Age + Genre + Critic_Score + Critic_Count + User_Count + Rating, data = train.set)
summary(model)

model$coefficients
```

## **OUTLIERS, LEVERAGE AND INFLUENTIAL POINTS**

```{r, warning=FALSE}
which(hatvalues(model) > 0.08)
plot(hatvalues(model),type="h"); abline(h=0.08)
which(cooks.distance(model)>1)
plot(cooks.distance(model),type="h"); abline(h=1)
```

## **DIAGNOSTIC CHECKING**

### **I. NORMALITY**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
qqnorm(residuals(model), ylab="Residuals")
qqline(residuals(model)) # Normality using Q-Q Plots
```

#### **2. Statistical Test**

**Ho**: ϵ’s normally distributed.

**Ha**: ϵ’s not normally distributed.

##### **2.1. Kolmogorov-Smirnov Test**

```{r, warning=FALSE}
resid_std <- scale(residuals(model)) # mean=0, sd=1
ks_test <- ks.test(resid_std, "pnorm") # Kolmogorov-Smirnov Test
ks_test
```

```{r, include=FALSE}
p_value = ks_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **the residuals are normally distributed.**" } else { "We reject the null hypothesis, therefore, **the residuals are not normally distributed.**" }`

### **II. HOMOSCEDASTICITY**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
plot(fitted(model), residuals(model))
```

#### **2. Statistical Test**

**Ho**: Heteroscedasticity is not present.

**Ha**: Heteroscedasticity is present.

##### **2.1. Breusch-Pagan-Godfrey Test**

```{r, warning=FALSE}
bp_test <- bptest(model) # Breusch-Pagan test
bp_test
```

```{r, include=FALSE}
p_value <- bp_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **Heteroscedasticity is not present.**" } else { "We reject the null hypothesis, therefore, **Heteroscedasticity is present.**" }`

### **III. MULTICOLINEARITY**

#### **1. Statistical Test**

```{r, warning=FALSE}
vif_values = vif(model)
vif_values
```

VIF > 5 -> **moderate concern**

VIF > 10 -> **serious multicollinearity**

```{r, echo=FALSE}
check_col <- vif_values[, ncol(vif_values)]

for (i in 1:length(check_col)) {
  var_name <- names(check_col)[i]
  val <- check_col[i]
  
  if (val > 5) {
    print(paste("WARNING:", var_name, "has moderate multicollinearity (VIF =", round(val, 2), ")"))
  } else if (val > 10) {
    print(paste("WARNING:", var_name, "has high multicollinearity (VIF =", round(val, 2), ")"))
  } else {
    print(paste(var_name, "is okay (VIF =", round(val, 2), ")"))
  }
}
```

### **IV. INDEPENDENCE**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
n = length(residuals(model))
plot(tail(residuals(model), n-1) ~
head(residuals(model), n-1),
xlab=expression(hat(epsilon)[i]),
ylab=expression(hat(epsilon)[i+1]))
abline(h=0, v=0, col = grey(0.5))
```

#### **2. Statistical Test**

**Ho**: No auto-correlation (the errors are uncorrelated)

**Ha**: There exists auto-correlation

##### **2.1. Durbin-Watson Test**

```{r, warning=FALSE}
dw_test = dwtest(model) # Durbin-Watson Test
dw_test
```

```{r, include=FALSE}
p_value <- dw_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **there is no auto-correlation.**" } else { "We reject the null hypothesis, therefore, **there exists auto-correlation.**" }`

## **DATA TRANSFORMATION (Logarithmic Model)**

Since the model is not normally distributed based on the results of the Kolmogorov-Smirnov test, we perform a data transformation using the **Logarithmic Model**.

```{r, warning=FALSE}
train.set$Log_Global_Sales <- log(train.set$Global_Sales)

model_log <- lm(Log_Global_Sales ~ Platform + Game_Age + Genre + 
                Critic_Score + Critic_Count + User_Count + Rating, 
                data = train.set)

summary(model_log)
```

## **DIAGNOSTIC CHECKING AFTER DATA TRANSFORMATION**

### **I. NORMALITY**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
qqnorm(residuals(model_log), ylab="Residuals")
qqline(residuals(model_log)) # Normality using Q-Q Plots
```

#### **2. Statistical Test**

**Ho**: ϵ’s normally distributed.

**Ha**: ϵ’s not normally distributed.

##### **2.1. Kolmogorov-Smirnov Test**

```{r, warning=FALSE}
resid_std <- scale(residuals(model_log)) # mean=0, sd=1
ks_test <- ks.test(resid_std, "pnorm") # Kolmogorov-Smirnov Test
ks_test
```

```{r, include=FALSE}
p_value = ks_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **the residuals are normally distributed.**" } else { "We reject the null hypothesis, therefore, **the residuals are not normally distributed.**" }`

### **II. HOMOSCEDASTICITY**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
plot(fitted(model_log), residuals(model_log))
```

#### **2. Statistical Test**

**Ho**: Heteroscedasticity is not present.

**Ha**: Heteroscedasticity is present.

##### **2.1. Breusch-Pagan-Godfrey Test**

```{r, warning=FALSE}
bp_test <- bptest(model_log) # Breusch-Pagan test
bp_test
```

```{r, include=FALSE}
p_value <- bp_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **Heteroscedasticity is not present.**" } else { "We reject the null hypothesis, therefore, **Heteroscedasticity is present.**" }`

### **III. MULTICOLINEARITY**

#### **1. Statistical Test**

```{r, warning=FALSE}
vif_values = vif(model_log)
vif_values
```

VIF > 5 -> **moderate concern**

VIF > 10 -> **serious multicollinearity**

```{r, echo=FALSE}
check_col <- vif_values[, ncol(vif_values)]

for (i in 1:length(check_col)) {
  var_name <- names(check_col)[i]
  val <- check_col[i]
  
  if (val > 5) {
    print(paste("WARNING:", var_name, "has moderate multicollinearity (VIF =", round(val, 2), ")"))
  } else if (val > 10) {
    print(paste("WARNING:", var_name, "has high multicollinearity (VIF =", round(val, 2), ")"))
  } else {
    print(paste(var_name, "is okay (VIF =", round(val, 2), ")"))
  }
}
```

### **IV. INDEPENDENCE**

#### **1. Graphical Analysis of Residuals**

```{r, warning=FALSE}
n = length(residuals(model_log))
plot(tail(residuals(model_log), n-1) ~
head(residuals(model_log), n-1),
xlab=expression(hat(epsilon)[i]),
ylab=expression(hat(epsilon)[i+1]))
abline(h=0, v=0, col = grey(0.5))
```

#### **2. Statistical Test**

**Ho**: No auto-correlation (the errors are uncorrelated)

**Ha**: There exists auto-correlation

##### **2.1. Durbin-Watson Test**

```{r, warning=FALSE}
dw_test = dwtest(model_log) # Durbin-Watson Test
dw_test
```

```{r, include=FALSE}
p_value <- dw_test$p.value
```

`r if(p_value >= 0.05) { "We fail to reject the null hypothesis, therefore, **there is no auto-correlation.**" } else { "We reject the null hypothesis, therefore, **there exists auto-correlation.**" }`

## VARIABLE SELECTION

```{r, warning=FALSE}
k<-ols_step_best_subset(model_log)
k
```

##### **Model 6** is the best model because despite it having a lesser R-Squared than Model 7, it still has the highest Adj. R-Square. It also has the lowest value of C(p), AIC, SBIC, and SBC.

## 3-FOLD CROSS VALIDATION

```{r, warning=FALSE}
# Define training control
train.control <- trainControl(method = "cv", number = 3)

model <- train(log(Global_Sales) ~ Platform + Game_Age + Genre + Critic_Score + Critic_Count + User_Count + Rating, data = data_df, method = "lm", trControl = train.control)

# Summarize the results
print(model)
```