---
title: "Testing"
author: "Group 2"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(RKaggle)
library(dplyr)
library(ggplot2)
library(car)
library(lmtest)
library(olsrr)

library(DT)
library(glmnet)
library(tibble)
library(forcats)
library(purrr)
library(readr)
library(stringr)
```

```{r, warning=FALSE}
data <- read.csv("../Video_Games_Sales_as_at_22_Dec_2016.csv",sep=",",na.strings=c(""," ","NA","N/A"))

data_row_count <- nrow(data)
```

#### Number of rows = **`r data_row_count`**

```{r, warning=FALSE}
# Show data
#head(data)
datatable(data[1:6,], 
          options = list(scrollX = TRUE, pageLength = 6),
          rownames = FALSE)


# Data cleaning
data <- na.omit(data)

na_row_count = data_row_count - nrow(data)
```

#### Number of rows with missing values = **`r na_row_count`**
#### New number of rows = **`r nrow(data)`**

```{r, warning=FALSE}
# Show data after dropping all NA values
#head(data)
datatable(data[1:6,], 
          options = list(scrollX = TRUE, pageLength = 6),
          rownames = FALSE)

str(data)

# Drop all sales except global
data_df <- cbind(data[,-c(6:10)],data$Global_Sales)
data_df$Year_of_Release <- 2016 - data_df$Year_of_Release
names(data_df)[3] <- "Game_Age"
names(data_df)[12] <- "Global_Sales"

str(data_df)

summary(data_df)
```

## REGRESSION MODEL

```{r, warning=FALSE}
set.seed(12)

reg_model <- data_df
str(reg_model)

# 70 : 30 RATIO
train.size <- floor(0.7*nrow(reg_model))
train.index <- sample(1:nrow(reg_model),train.size, replace = F)
train.set <- reg_model[train.index,]
test.set <- reg_model[-train.index,]
```

```{r, warning=FALSE}
model <- lm(Global_Sales ~ Critic_Score + Critic_Count + User_Count, data = train.set)
summary(model)

model$coefficients

# Diagnostic Checking
par(mfrow = c(2, 2))
plot(model)

# Outliers, Leverage and Influential Points
which(hatvalues(model) > 0.08)
plot(hatvalues(model),type="h"); abline(h=0.08)
which(cooks.distance(model)>1)
plot(cooks.distance(model),type="h"); abline(h=1)
```

```{r, warning=FALSE}
model <- lm(formula = Global_Sales ~ Platform + Game_Age + Genre + Critic_Score + Critic_Count + User_Count + Rating, data = train.set)
summary(model)

model$coefficients

# Diagnostic Checking
par(mfrow = c(2, 2))
plot(model)

# Outliers, Leverage and Influential Points
which(hatvalues(model) > 0.08)
plot(hatvalues(model),type="h"); abline(h=0.08)
which(cooks.distance(model)>1)
plot(cooks.distance(model),type="h"); abline(h=1)
```

## VARIABLE SELECTION

```{r, warning=FALSE}
k<-ols_step_best_subset(model)
k
```

##### **Model 7** is the best model because it has the highest R-Square, Adj. R-Square, and Pred R-Square. It also has the lowest value of C(p), AIC, SBIC, and SBC

## EVALUATION OF REGRESSION MODEL

### I. RIDGE REGRESSION

```{r, warning=FALSE}
X_full <- model.matrix(Global_Sales ~ Platform + Game_Age + Genre + 
                         Critic_Score + Critic_Count + User_Count + Rating, 
                       data = reg_model)[, -1]
y_full <- reg_model$Global_Sales

X_train <- X_full[train.index, ]
X_test  <- X_full[-train.index, ]
y_train <- y_full[train.index]
y_test  <- y_full[-train.index]
```

```{r, warning=FALSE}
ridge_cv <- cv.glmnet(
  X_train, y_train,
  alpha = 0
)

#Predictions
ridge_pred_train <- predict(ridge_cv, X_train, s = "lambda.min")
ridge_pred_test <- predict(ridge_cv, X_test, s = "lambda.min")

# RMSE
ridge_rmse_train <- sqrt(mean((y_train - ridge_pred_train)^2))
ridge_rmse_test <- sqrt(mean((y_test - ridge_pred_test)^2))

ridge_rmse_train
ridge_rmse_test
```

### II. LASSO REGRESSION

```{r, warning=FALSE}
lasso_cv <- cv.glmnet(
  X_train, y_train,
  alpha = 1
)

#Predictions
lasso_pred_train <- predict(lasso_cv, X_train, s = "lambda.min")
lasso_pred_test <- predict(lasso_cv, X_test, s = "lambda.min")

# RMSE
lasso_rmse_train <- sqrt(mean((y_train - lasso_pred_train)^2))
lasso_rmse_test <- sqrt(mean((y_test - lasso_pred_test)^2))

lasso_rmse_train
lasso_rmse_test
```

### III. COMPARISON TABLE

```{r, warning=FALSE}
rmse_results <- data.frame(
  Model = c("Ridge", "LASSO"),
  Train_RMSE = c(ridge_rmse_train, lasso_rmse_train),
  Test_RMSE = c(ridge_rmse_test, lasso_rmse_test)
)
rmse_results
```

